---
title: "igem_part.Rmd"
author: Emelianov Georgii
output:
  pdf_document: default
  html_document: default
---
```{r, echo=FALSE}
no <- c(1, 2, 3, 4, 5)

team_name <- c("NEFU-China", "Moscow", "EPFL", "Queens-Canada", "Nantes")

project_title <- c("BOLD", "HaploSense", "Espress'EAU", "Velcrion", "The A3 project")

project_year <- c("2020", "2020", "2020", "2020", "2020")

wiki_page <- c("https://2020.igem.org/Team:NEFU_China", " https://2020.igem.org/Team:Moscow", "https://2020.igem.org/Team:EPFL", "https://2020.igem.org/Team:Queens_Canada", "https://2020.igem.org/Team:Nantes")

igem_team <- data.frame(no, team_name, project_title, project_year, wiki_page)

#knitr::kable(std, format="markdown")
knitr::kable(igem_team)
```

```{r, echo=FALSE}
no <- c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13)

part_id <- c("BBa_K1316002",
"BBa_K2559005",
"BBa_K3457012", 
"BBa_K3350857", 
"BBa_K2913020", 
"BBa_K2913022", 
"BBa_K216008", 
"BBa_K322312", 
"BBa_K1316006", 
"BBa_K3350859", 
"BBa_K3350860", 
"BBa_K3350862", 
"BBa_K3350858")

part_name <- c("yqjF",
"EGFP",
"Cytosolic-abundant heat soluble protein 106094",
"yhaJ",
"TrrnB",
"pBAD",
"LuxAB",
"LuxCDE",
"nemA-nfsA-nfsB",
"yqjF1st",
"yqjF2nd",
"yqjF3rd",
"yhaJ1st")

part_type <- c("Promoter",
"Coding",
"Coding",
"Coding",
"Terminator",
"Promoter",
"Coding",
"Coding",
"Coding",
"Promoter",
"Promoter",
"Promoter",
"Coding")

team_id <- c(1,1,1,1,1,1,1,1,1,1,1,1,1)

igem_part <- data.frame (no, part_id, part_name, part_type, team_id)
knitr::kable(igem_part)
```



```{r, echo=FALSE}
no <- c(1)

part_id <- c("BBa_K3636000")

part_name <- c("CasX (Cas12e)")

part_type <- c("Coding")

team_id <- c(2)

igem_part <- data.frame (no, part_id, part_name, part_type, team_id)
knitr::kable(igem_part)
```

```{r, echo=FALSE}
no <- c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15, 16, 17)

part_id <- c("BBa_K3600000",
"BBa_K3600001",
"BBa_K3600002",
"BBa_K3600003",
"BBa_K3600004",
"BBa_K3600006",
"BBa_K3600007",
"BBa_K3600008",
"BBa_K3600009",
"BBa_K3600010",
"BBa_K3600011",
"BBa_K3600012",
"BBa_K3600013",
"BBa_K3600014",
"BBa_K3600015",
"BBa_K3600016",
"BBa_K3600017")

part_name <- c("HSP12 promoter part plasmid",
"TRX2 promoter part plasmid",
"YCF1 promoter part plasmid",
"GSH1 promoter part plasmid",
"GLR1 promoter part plasmid",
"prHSP12-yomScarlet-I-tADH1",
"prTRX2-yomScarlet-I-tADH1",
"prYCF1-yomScarlet-I-tADH1",
"prGSH1-yomScarlet-I-tADH1",
"mScarlet-I reporter gene",
"prGLR1-yomScarlet-I-tADH1",
"Lys2-GFP dropout multi-gene backbone",
"Lys2-HSP12pr-mScarleti cassette",
"Lys2-TRX2pr-mScarleti cassette",
"Lys2-YCF1pr-mScarleti cassette",
"Lys2-GSH1pr-mScarleti cassette",
"Lys2-GLR1pr-mScarleti cassette")


part_type <- c("Regulatory",
"Regulatory",
"Regulatory",
"Regulatory",
"Regulatory",
"Cassette",
"Cassette",
"Cassette",
"Cassette",
"Reporter",
"Cassette",
"Cassette",
"Cassette",
"Cassette",
"Cassette",
"Cassette",
"Cassette")

team_id <- c(3, 3, 3, 3, 3, 3, 3, 3, 3, 3, 3, 3, 3, 3, 3, 3, 3)

igem_part <- data.frame (no, part_id, part_name, part_type, team_id)
knitr::kable(igem_part)
```


```{r, echo=FALSE}
no <- c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15, 16)

part_id <- c("BBa_K3515000",
"BBa_K3515001",
"BBa_K3515002",
"BBa_K3515003",
"BBa_K3515004",
"BBa_K3515005",
"BBa_K3515006",
"BBa_K3515007",
"BBa_K3515008",
"BBa_K3515009",
"BBa_K3515010",
"BBa_K3515011",
"BBa_K3515012",
"BBa_K3515013",
"BBa_K3515014",
"BBa_K3515015")

part_name <- c("E coil alpha helix with cysteine to be used with a K coil alpha helix for protein immobilization",
"K coil alpha helix with cysteine to be used with a E coil alpha helix for protein immobilization",
"Synechococcus Phosphate Binding Protein with cysteine modification(s) to bind to a biosensor",
"Troponin C, a calcium binding protein with cysteine modification(s) to bind to a biosensor",
"Potassium binding protein with cysteine modification(s) to bind to a biosensor",
"Glucose binding protein with cysteine modification(s) to bind to a biosensor",
"Synechococcus Phosphate Binding Protein with cysteine modification(s) and FRET to monitor phosphate",
"Troponin C, a calcium binding protein with cysteine modification(s) to bind to a biosensor and FRET",
"Potassium binding protein with cysteine modification(s) to bind to a biosensor and FRET to monitor p",
"Glucose binding protein with cysteine modification(s) to bind to a biosensor and FRET to monitor glu",
"Vitamin D Receptor Binding Protein with cysteine modification(s) to bind to a biosensor",
"Vitamin D receptor binding protein with cysteine modification(s) to bind to a biosensor and FRET to",
"Parathyroid Hormone Receptor with cysteine modification(s) to bind to a biosensor",
"Parathyroid Hormone Receptor with cysteine modification(s) and FRET to monitor PTH levels using a b",
"Alpha-Klotho Binding Protein with cysteine modification(s) to bind to a biosensor",
"Alpha-Klotho Binding Protein with cysteine modification(s) and FRET to monitor phosphate levels usin")


part_type <- c("Coding",
"Coding",
"Coding",
"Coding",
"Coding",
"Coding",
"Coding",
"Coding",
"Coding",
"Coding",
"Coding",
"Coding",
"Coding",
"Coding",
"Coding",
"Coding")


team_id <- c(4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4)

igem_part <- data.frame (no, part_id, part_name, part_type, team_id)
knitr::kable(igem_part)